The Driving Forces of API Evolution

### 2015-06-02 thesis/paper.tex
Small section on APIs

\subsection{APIs} \label{api_design}
%define what an API is for us
%we consider APIs to be systems because x y z \cite{761853,5733835} 
%Introduce different layers of an API.
%Headers / Interfaces
%Implementation
%"Middle Layer"

@@

Software evolution theory suggests that software programs can be grouped into three different types of systems, namely S-programs, P-programs and E-programs \cite{lehman1980programs}. S-programs are programs which are exactly derivable from a specification. An example of such a program is one which finds the lowest common denominator for two integers. A key characteristic of an S-program is that if its functionality is changed, the end product will be a new product and not an evolved version of the previous program, since the mapping between specification and program is exact. P-programs are programs which are inherently more complex, and ``solve a problem which can be precisely formulated, but whose solution must inevitably reflect an approximation of the real world''. Furthermore, P-programs are programs which are centered around the perception of users, analysts and/or programmers. This perception is often commonly a mathematical model of the problem. An example of such a program is a program which predicts weather, since it is derived from a set of hydrodynamic equations. E-programs are described as ``inherently even more change prone [than S-programs and P-programs]. They are programs that mechanize a human or societal activity''. These factors can be explained by the difference between P-programs and a E-programs which is that E-programs ``change the very nature of the problem to be solved'' by ``becoming a part of the world it models''. Further, a characteristic of E-programs is that, during development, the specification must be developed by involving predictions of the consequences of the deployment of that system will have, since once the program is deployed ``questions of correctness, appropriateness, and satisfaction arise which inevitably leads to additional pressure for change". Lehman's eight laws of software evolution are said to apply to such E-programs. The laws are presented in Table \ref{table:expl_laws}.

>>>>

\subsection{APIs} \label{api_design}
%what is an API
An API offers an interface through which developers can use to access functionality of a system. APIs can be seen as having three interacting layers; the interfaces, the implementation and additional functionality. Typically, the interfaces provide the definitions of functions and data structures while the implementation realises those interfaces. The additional functionality exists as a middle layer that provides things such as error handling, third party libraries and additional auxiliary features.
%we consider APIs to be systems because x y z \cite{761853,5733835}
Given that there is a combination of different interacting elements that does not only concern interfaces to implementations, we would argue that an API can be described as a system \cite{761853,5733835}.
%Introduce different layers of an API.
%Headers / Interfaces
%Implementation
%"Middle Layer"

@@

Software evolution theory suggests that software programs can be grouped into three different types of systems, namely S-programs, P-programs and E-programs \cite{lehman1980programs}. S-programs are programs which are exactly derivable from a specification. An example of such a program is one which finds the lowest common denominator for two integers. A key characteristic of an S-program is that if its functionality is changed, the end product will be a new product and not an evolved version of the previous program, since the mapping between specification and program is exact. P-programs are programs which are inherently more complex, and ``solve a problem which can be precisely formulated, but whose solution must inevitably reflect an approximation of the real world''. Furthermore, P-programs are programs which are centred around the perception of users, analysts and/or programmers. This perception is often commonly a mathematical model of the problem. An example of such a program is a program which predicts weather, since it is derived from a set of hydrodynamic equations. E-programs are described as ``inherently even more change prone [than S-programs and P-programs]. They are programs that mechanize a human or societal activity''. These factors can be explained by the difference between P-programs and a E-programs which is that E-programs ``change the very nature of the problem to be solved'' by ``becoming a part of the world it models''. Further, a characteristic of E-programs is that, during development, the specification must be developed by involving predictions of the consequences of the deployment of that system will have, since once the program is deployed ``questions of correctness, appropriateness, and satisfaction arise which inevitably leads to additional pressure for change". Lehman's eight laws of software evolution are said to apply to such E-programs. The laws are presented in Table \ref{table:expl_laws}.
